From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-09 Pi+/paper/reversible1.tex

\noindent where the first level-2 combinator states the obvious fact that compositions with the identity can be
optimized and the second level-2 combinator states the more interesting observation that swapping the two sides of a sum
type and then applying $c_1$ to the left and $c_2$ to the right is equivalent to applying $c_2$ to the left and $c_1$ to
the right and then swapping. The full set of level-2 combinators is large and is only listed in the accompanying code.

>>>>

\noindent where the first level-2 combinator states the obvious fact that compositions with the identity can be
optimised and the second level-2 combinator states the more interesting observation that swapping the two sides of a sum
type and then applying $c_1$ to the left and $c_2$ to the right is equivalent to applying $c_2$ to the left and $c_1$ to
the right and then swapping. The full set of level-2 combinators is large and is only listed in the accompanying code.
